DeepSphere: Efficient spherical Convolutional Neural Network with HEALPix sampling for cosmological applications

### 2019-02-26 rebuttal.tex

%left in column
\newcommand{\lcol}[1]{%
\begin{minipage}[t]{.35\textwidth}%

#1%

\end{minipage}%
}

\title{\vspace{-1cm}
\begin{flushleft} {\sffamily Rebuttal for paper \emph{ASCOM\_2018\_119} }\end{flushleft}}
\date{\vspace{-1.7cm}\begin{flushleft}\sffamily DeepSphere: Efficient spherical Convolutional Neural Network with HEALPix sampling for cosmological applications, Nathanaël Perraudin, Michaël Defferrard, Tomasz Kacprzak, Raphael Sgier \end{flushleft}}

@@

% MATH SYMBOLS
\newcommand{\1}{\b{1}}              % all-ones vector
\newcommand{\0}{\b{0}}              % all-zero vector
\newcommand{\g}[1]{\b{#1}}
\newcommand{\G}{\mathcal{G}}
\newcommand{\V}{\mathcal{V}}
\newcommand{\E}{\mathcal{E}}
\newcommand{\C}{\mathcal{C}}
\newcommand{\B}{\mathcal{B}}
\renewcommand{\L}{\b{L}}
\newcommand{\tL}{\tilde{\L}}
\newcommand{\W}{\b{W}}
\newcommand{\I}{\b{I}}
\newcommand{\D}{\b{D}}
\newcommand{\U}{\b{U}}
\newcommand{\x}{\b{x}}
\newcommand{\X}{\b{X}}
\newcommand{\y}{\b{y}}
\newcommand{\Y}{\b{Y}}
\newcommand{\bu}{\b{u}}
\newcommand{\f}{\b{f}}
\newcommand{\trans}{^\intercal}
\newcommand{\R}{\mathbb{R}}
\newcommand{\bLambda}{\b{\Lambda}}
\newcommand{\blambda}{\b{\lambda}}
\newcommand{\bO}{\mathcal{O}}
\newcommand{\T}{\mathcal{T}}
\DeclareMathOperator*{\esp}{E}
\DeclareMathOperator*{\var}{Var}
\DeclareMathOperator*{\vect}{vec}
\DeclareMathOperator*{\argmin}{arg \, min}
\newcommand{\pkg}[1]{\texttt{#1}}

\begin{document}
\maketitle

% Note: it is very convenient to refer to other comments using the referencing system of \LaTeX, such as here see  \autoref{comment:errorEq2}.

The authors would like to thank the reviewers for their time and comments, which significantly helped improve the manuscript.
We believe we addressed all the raised issues in the following rebuttal.

### 2019-02-26 rebuttal.tex

\begin{mdframed}[style=comment]
I should say, even though I made the above comments, I thought the paper was really excellent and well written. There were a couple of very minor points which I would like the authors to expand slightly on or consider.
\end{mdframed}
Thank you very much for your comments. We addressed them to the best we could.

\subsection{}
\begin{mdframed}[style=comment]
While our construction will not exactly respect the setting defined by [33], we observe empirically strong evidence of convergence.

- Could you add a plot comparing the graph Laplacian as a function of number of pixels and the Laplace-Beltrami operator so the reader can explicitly see the convergence?
\end{mdframed}

Good point.
To experimentally show convergence, we would need to build a series of graph Laplacians that converges to the Laplace-Beltrami operator.
This is complicated and requires to solve the theoretical problem first.
Hence, we built one Laplacian and observed some similarities between the two operators instead.
We agree that our wording was unfortunate and have modified the manuscript to mean that we empirically observed a strong correspondence rather than a proper convergence.
The convergence (or even exact correspondence) is a problem we are currently investigating and plan to release as a separate contribution.
See also comment 1.4 and our answer there.

\todo{the new figure A.12 is maybe a weak proof of convergence}

\mdeff{@nati, what do you think?}

### 2019-02-26 rebuttal.tex

\subsection{}

\begin{mdframed}[style=comment]
We found out that the one proposed above works well for our purpose, and did not investigate other approaches, leaving it to future work.

- Are you really going to search through different weighting schemes in future work? I would be interested if you were, but could you speculate on what you expect to achieve by looking at different ones?
\end{mdframed}

Yes, we are investigating how to best set the edge weights (the sole degree of freedom when building a graph).
The question is: what edge weights should be set such that the graph Laplacian converges (or is equivalent) to the Laplace-Beltrami (up to a certain bandwidth).
Ideally, that should work for any sampling of the sphere.
(Equivalently, the Fourier modes converge or are equivalent to the spherical harmonics.)
A proof of convergence or equivalence would allow a graph convolution that is truly equivariant to rotation.
Moreover, it would enable to do high-precision filtering using the graph rather than the SHT (for speed).
See also comment 1.6 and our answer there.

% \nati{@michael, how much shall we say here?}
% \mdeff{I like to be open. It's mostly written in the paper anyway.}

### 2019-02-26 scnn.tex
comment 2.5

As a future work, it would be interesting to further investigate the link between the graph Fourier basis and the spherical harmonics.
Furthermore, the influence of irregular sampling on the convolution's equivariance to rotation should be empirically quantified and ideally theoretically bounded.
Further comparison of DeepSphere to other spherical CNN formulations, with different sampling schemes, would also be worthwhile.

>>>>

As future work, it would be interesting to further investigate the relation between the graph Fourier basis and the spherical harmonics.
The goal would be to find edge weights such that the graph Laplacian converges (or is equivalent) to the Laplace-Beltrami (up to a certain bandwidth).
Ideally, that should work for any sampling of the sphere.
That would enable a truly rotation equivariant graph convolution and high-precision filtering using the graph rather than the SHT (for speed).
% Furthermore, the influence of irregular sampling on the convolution's equivariance to rotation should be empirically quantified and ideally theoretically bounded.
Finally, a comparison of DeepSphere to other spherical CNN formulations, with different sampling schemes, would be worthwhile.
